Quality Assesment of OpenStreetMap Footpath Data for 3D City Recreation

### 2020-06-04 report/report.tex
Specify todo about problem specification in the introduction, do this lates when the layout is done

When it comes to the quality of available data, it turns out that in practise, 3D GIS datasets without errors are rare.
Among the most common errors are missing or invalid geometry, and invalid semantics.
However, \textbf{(Biljecki et al, 2016)} note that there are coming more and more sophisticated methods for automatically correcting the most common errors.
GIS validation and correction is only an emerging field of research.
and many such datasets were usually obtained years ago, and creating error-free datasets was neither possible due to the lack of validation techniques, nor a high priority.

@@

% Torsdag:
% TODO: Move content from chapters 1, 3 and 4 to Background
% TODO: Mention that positional accuracy will be the focus early on

>>>>

% TODO: Mention that positional accuracy will be focused on, and the implications of not fixing errors when converting to a 3D model
When it comes to the quality of available data, it turns out that in practise, geodata databases without errors are rare.
Among the most common errors are missing or invalid geometry, and invalid semantics.
However, \textbf{(Biljecki et al, 2016)} note that there are coming more and more sophisticated methods for automatically correcting the most common errors.
Geodata validation and correction is only an emerging field of research.
and many such datasets were usually obtained years ago, and creating error-free datasets was neither possible due to the lack of validation techniques, nor a high priority.

@@
